Towards a classification framework for social machines

### 2013-02-21 latex/paper_new.tex
related work

A Social Machine includes human and machine two major components, therefore, the study of social machine is an interdisciplinary endeavour. Since the Turning machine was invented, there has been a `paradigm shift' in using computers, where the computer facilitates human communication rather acts as a purely calculative device. The Computer-supported Collaboration Work (CSCW) emerged in 1982 represent such shift. It addresses ``how collaborative activities and their coordination can be supported by means of computer systems'' later evolved in a more broader sense of  Computer-supported collaboration (CSC). The Social computing is another shift, which is a generic term refers systems that support ``the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets''. To compare with the CSC, the social computing has more focus in computing rather than broader sense of

>>>>

A Social Machine includes human and machine two major components, therefore, the study of social machine is an interdisciplinary endeavour. Since the Turning machine was invented, there has been a `paradigm shift' in using computers, where the computer facilitates human communication rather acts as a purely calculative device. The Computer-supported Collaboration Work (CSCW) emerged in 1982 represent such shift. It addresses ``how collaborative activities and their coordination can be supported by means of computer systems'' later evolved in a more broader sense of  Computer-supported collaboration (CSC). The Social computing is another shift, which is a generic term refers systems that support ``the gathering, representation, processing, use, and dissemination of information that is distributed across social collectivities such as teams, communities, organizations, and markets''. To compare with the CSC, the social computing has more focus in `computing' rather than `collaboration'. Similarly, the Human Computation is another paradigm towards this computational direction, it utilize human processing power to solve problems that computers cannot yet solve. All these three mentioned fields has overlapping in the their concepts and they are only mainly popularised in the computer science. In the Web 2.0 era, there are few new concepts/buzzword emerged
